The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-07-29 brains-protocol.tex
fix/todos: fix small cosmetic changes, comment out an appendix-related sentence

Since our data is about written transformations, number of letters and orthographic neighborhood density are the natural representatives of groups (a) and (b) respectively.
Given the importance of age of acquisition in the lexical feature literature, we chose it to represent group (c).
Finally we used clustering coefficient to represent group (d) since it has already been used in previous studies.
The final set of features we will discuss in the rest of the paper, as well as their cross-correlations, can be seen in Fig.~\ref{fig:feature-corrs-filtered} (the analysis on the complete set of features can be found in the appendix).\footnote{
Note that feature values stem from different data sets which do not always encode the same words.
Indeed, we have data on frequency for about \newtext{33.5k} words, on age of acquisition for 30.1k words, on clustering coefficient for 5.7k words, number of synonyms 111.2k, and \newtext{orthographic density 17.8k words}.
Quite often then, not all features are available for all words in our data set;
however this is not problematic since the analysis is done on a per-feature basis, and not all words need be encoded in all features.}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/all-susceptibilities-pos.png}
    \caption{\newtext{\textbf{Substitution susceptibility for POS categories:} categories are simplified from the TreeTagger tag set: \emph{J} means adjective, \emph{N}~noun, \emph{R}~adverb, \emph{V}~verb, and \emph{Stopword-like} gathers together all the categories partially or completely affected by the stopword filter (see main text for details).
    The top panel shows the actual $s_{POS}$ and $s_{POS}^0$ counts, the bottom panel shows $\sigma_{POS}$, the ratio of the two.
    Confidence intervals are computed with the Goodman method for multinomial proportions.}
    \todo{Split into 2 subfigures; fix labels; use log-y for second pane; add H0 dashed line.}}
    \label{fig:pos-susceptibilities}
\end{figure}

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/paper-susceptibilities-quantilebins_global.png}
    \caption{\textbf{Substitution susceptibility for feature values:}
    susceptibility to substitution versus feature value of a candidate word for substitution \newtext{(binned by quartiles)}, with 95\% asymptotic confidence intervals \newtext{(Goodman-based multinomial)}.
    \todo{Use log-y}
    }
    \label{fig:feature-susceptibilities-global}
\end{figure*}

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/paper-variations-quantilebins_sentencerel.png}
    \caption{\newtext{\textbf{Sentence-relative feature variation:}
    $\nu_{\phi_r}$, average sentence-relative feature value of the appearing word as a function of the sentence-relative value of the disappearing word (binned by quartiles), with 95\% asymptotic confidence intervals based on Student's \emph{t}-distribution.
    $\nu_{\phi_r}^0$ and $\nu_{\phi_r}^{00}$ are similarly converted to be sentence-relative.
    Attraction, magnitude and direction of bias with respect to null hypotheses are similar to Fig.~\ref{fig:feature-variations-global}.
    However, attractors are always positioned between sentence median ($y=0$) on one side and $\nu_{\phi_r}^0$ and $\nu_{\phi_r}^{00}$ on the other side.
    Clustering coefficient, Number of synonyms and Orthographic neighborhood density are limit cases, with triple intersections with one of the null hypothesis curves.
    }
    \todo{fix labels}
    }
    \label{fig:feature-variations-sentencerel}
\end{figure*}

>>>>

Since our data is about written transformations, number of letters and orthographic neighborhood density are the natural representatives of groups (a) and (b) respectively.
Given the importance of age of acquisition in the lexical feature literature, we chose it to represent group (c).
Finally we used clustering coefficient to represent group (d) since it has already been used in previous studies.
The final set of features we will discuss in the rest of the paper, as well as their cross-correlations, can be seen in Fig.~\ref{fig:feature-corrs-filtered}.% (the analysis on the complete set of features can be found in the appendix).
\footnote{
Note that feature values stem from different data sets which do not always encode the same words.
Indeed, we have data on frequency for about \newtext{33.5k} words, on age of acquisition for 30.1k words, on clustering coefficient for 5.7k words, number of synonyms 111.2k, and \newtext{orthographic density 17.8k words}.
Quite often then, not all features are available for all words in our data set;
however this is not problematic since the analysis is done on a per-feature basis, and not all words need be encoded in all features.}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/all-susceptibilities-pos.png}
    \caption{\newtext{\textbf{Substitution susceptibility for POS categories:} categories are simplified from the TreeTagger tag set: \emph{J} means adjective, \emph{N}~noun, \emph{R}~adverb, \emph{V}~verb, and \emph{Stopword-like} gathers together all the categories partially or completely affected by the stopword filter (see main text for details).
    The top panel shows the actual $s_{POS}$ and $s_{POS}^0$ counts, the bottom panel shows $\sigma_{POS}$, the ratio of the two.
    Confidence intervals are computed with the Goodman method for multinomial proportions.}
    }
    \label{fig:pos-susceptibilities}
\end{figure}

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/paper-susceptibilities-quantilebins_global.png}
    \caption{\textbf{Substitution susceptibility for feature values:}
    susceptibility to substitution versus feature value of a candidate word for substitution \newtext{(binned by quartiles)}, with 95\% asymptotic confidence intervals \newtext{(Goodman-based multinomial)}.
    }
    \label{fig:feature-susceptibilities-global}
\end{figure*}

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/paper-variations-quantilebins_sentencerel.png}
    \caption{\newtext{\textbf{Sentence-relative feature variation:}
    $\nu_{\phi_r}$, average sentence-relative feature value of the appearing word as a function of the sentence-relative value of the disappearing word (binned by quartiles), with 95\% asymptotic confidence intervals based on Student's \emph{t}-distribution.
    $\nu_{\phi_r}^0$ and $\nu_{\phi_r}^{00}$ are similarly converted to be sentence-relative.
    Attraction, magnitude and direction of bias with respect to null hypotheses are similar to Fig.~\ref{fig:feature-variations-global}.
    However, attractors are always positioned between sentence median ($y=0$) on one side and $\nu_{\phi_r}^0$ and $\nu_{\phi_r}^{00}$ on the other side.
    Clustering coefficient, Number of synonyms and Orthographic neighborhood density are limit cases, with triple intersections with one of the null hypothesis curves.}
    }
    \label{fig:feature-variations-sentencerel}
\end{figure*}
